\documentclass[12pt]{article}
\input{pott}
\begin{document}\begin{pottproblem}
\textbf{Problem 903}

Imagine that you have a very, very rigid, thin, solid, circular ring of mass $M$ and radius $a$.
You spin it at an angular frequency $\omega$ around its axis of symmetry.
What happens as the tangential speed $\omega\,a$ approaches the speed of light $c$?

\textsl{(a)} The most straightforward answer is: The ring contracts, because of length contraction.
If this is true, what is its new radius $a'$ as a function of $\omega$?

\textsl{(b)} But wait: How rigid can a ring be? What is the fastest possible speed of
longitudinal waves in the ring?

\textsl{(c)} The speed of a longitudinal wave depends on the density $\rho$ of the ring and its
bulk modulus $K$. The modulus has units of pressure (it is technically stress per unit dimensionless strain).
What, therefore is the highest bulk modulus $K_\mathrm{max}$ the ring can possibly have?

\textsl{(d)} Imagine that the ring has bulk modulus approaching $K_\mathrm{max}$.
That makes the ring elastic, and therefore stretchy.
How stretchy? Does it shrink more (because of length contraction) or stretch more (because of elasticity)
when spun at a relativistic frequency $\omega$?
That is, will $a'$ be greater or less than $a$ as $\omega$ approaches $c/a$?

\textsl{(e)} Diamond is pretty stiff. But nowhere near stiff enough to be relevant here.
What could conceivably be stiff enough to be a good material out of which to make this ring?
\textsl{Hint:} You might need a topological defect!

\end{pottproblem}\end{document}
